% resume.tex
%
% (c) 2007-2011 Jeremy B. R. Edberg <jedberg@gmail.com> http://www.jedberg.net
%

%%%%%%%%%%%%
% Basic setup
\documentclass[11pt]{article}
\usepackage{fullpage}
\usepackage{setspace}
\pagestyle{empty}
\setlength{\tabcolsep}{0in}
\hyphenchar\font=-1
\usepackage{geometry} 
\geometry{legalpaper, twoside} 
\setstretch{1}
\usepackage{booktabs}
\usepackage{topcapt}
%\raggedbottom
%\raggedright
\usepackage{tabulary}
\usepackage{hyphenat}
%%%%%%%%%%%%

%%%%%%%%%%%%
% PDF setup
\usepackage{ifpdf}
\ifpdf
  \usepackage[pdftex]{hyperref}
\else
  \usepackage[hypertex]{hyperref}
\fi
\hypersetup{
    letterpaper,
    colorlinks,
    urlcolor=black,
    pdfpagemode=none,
    pdftitle={Resume},
    pdfauthor={Igor Terzic},
    pdfsubject={Resume},
    pdfkeywords={reddit, eBay, python, pylons, unix, product, Engineering Leadership, cloud computing, virtualization, Unix/Linux administration, security, general technical operations, web development, UC Berkeley, Technology vision, scalable systems, highly reliable systems, enterprise computing, web architectures, web services, operating systems, systems management}
}
%%%%%%%%%%%%

%%%%%%%%%%%%
% Margin setup
\oddsidemargin  -0.5in
\evensidemargin -0.5in
\textwidth      7.2in
\headheight     -0.7in
\topmargin      0.0in
\textheight=13.0in
%\footheight 1.0in 
%%%%%%%%%%%%

\begin{document}

%% Heading
\begin{center}
\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}lcr}
&{\textbf{\sc{Igor Terzic Resum\'e}}}&\\
terzicigor@gmail.com  &  & Mobile: (406) 640-3190\\
\hline\hline
\end{tabular*}
\end{center}

%% Experience Section

% reddit
\noindent 
\\
%\\
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{reddit.com} & San Francisco, CA \\
\emph{Chief Architect and Lead Technologist} & \emph{January 2011 to Present} \\
\emph{Operations Manager} & \emph{March 2007 to January 2011}
\end{tabular*}
{\small

\noindent
\begin{list}{$\bullet$}{
%\setlength{\itemsep}{ -5pt}
%\setlength{\partopsep}{ -18pt}
}
\item Responsible for all technology -- system architecture, hiring, managing, capacity planning, budgeting, operations, vendors, maximizing automation while minimizing infrastructure.  Oversaw a 30X traffic growth and a five-fold growth in infrastructure.  Expert in virtualized environments (aka Cloud Computing) and rapid website scaling.
\item  Involved in the design and testing of all major site features, marketing, determining new product directions and ideas,  writing open source code, promotion, management of a 18M+ user community, etc.  
\item Expert on the system end-to-end, requiring learning and integrating new technologies quickly.  
\item Built the tools to support 1B+ page views per month with just one system administrator -- a set of tools to reduce code deployment time from 30 minutes to 1 minute; a monitoring infrastructure to send alerts before problems become critical, including self-healing to minimize operator involvement; tools to monitor traffic in real-time.  
\item Planned and carried out a move of reddit's servers from Boston to San Francisco with no downtime and then 1.5 years later planned and executed a move of reddit's servers from colocated hosting to Amazon's EC2.
\item Designed, implemented and currently maintain a white-label embedable voting widget based on reddit technology that brings in millions of dollars in revenue annually. Used for interactive advertising that was nominated for the Best Interactive Advertising Webby Award.
\end{list}
}


% eBay
\noindent
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{eBay, Inc.} & San Jose, CA \\
\emph{Senior Systems Engineer} & \emph{July 2006 to March 2007} \\
\emph{Senior Information Security Engineer} & \emph{July 2003 to June 2006}
\end{tabular*}
{\small
\noindent
\begin{list}{$\bullet$}{
%\setlength{\itemsep}{ -5pt}
%\setlength{\partopsep}{ -18pt}
}
\item Responsible for the daily operation of eBay's development lab.  Projects in the lab were Proof-of-Concepts for hardware and software with bleeding edge technology  and worked closely with the developers and architects to help plan what eBay's hardware will look like in a three year time-frame.
\item Protected 210+ million users from external threats and the security of the largest transactional e-commerce system in the world.  Developed fraud detection and prevention software (patent pending); investigated computer crime; ran  the IDS and log aggregation/correlation system; served as a security consultant for the entire organization as well as customers.  Developed and tested the fraud prevention technology in the eBay toolbar.
\item Deployed eBay's authenticated email infrastructure: created our Sender Policy Framework entries, defining eBay's record as the standard format for large mail installations.  Worked with vendors to define the DKIM standard and create use cases. 
\item Designed and developed an automated Sarbanes-Oxley (SOX) data collection program in Perl to replace the scripts provided by Price Waterhouse Coopers, saving the company thousands of dollars
\end{list}
}

% Sendmail
\noindent 
\\
% Yellow Phoenix
\noindent 
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Addepar} & Mountain View, CA \\
\emph{Software Engineer} & \emph{June 2012-June 2013} \\
\emph{Ember.js and Ember-Data consultant} & \emph{June 2013-May 2014}
\end{tabular*}
{\small
\noindent
\begin{list}{$\bullet$}{
%\setlength{\itemsep}{ -5pt}
%\setlength{\partopsep}{ -18pt}
}
\item Responsible for the daily operation of eBay's development lab.  Projects in the lab were Proof-of-Concepts for hardware and software with bleeding edge technology  and worked closely with the developers and architects to help plan what eBay's hardware will look like in a three year time-frame.
\item Protected 210+ million users from external threats and the security of the largest transactional e-commerce system in the world.  Developed fraud detection and prevention software (patent pending); investigated computer crime; ran  the IDS and log aggregation/correlation system; served as a security consultant for the entire organization as well as customers.  Developed and tested the fraud prevention technology in the eBay toolbar.
\item Deployed eBay's authenticated email infrastructure: created our Sender Policy Framework entries, defining eBay's record as the standard format for large mail installations.  Worked with vendors to define the DKIM standard and create use cases. 
\item Designed and developed an automated Sarbanes-Oxley (SOX) data collection program in Perl to replace the scripts provided by Price Waterhouse Coopers, saving the company thousands of dollars
\end{list}
}


% Yellow Phoenix

% Yellow Phoenix
\noindent 
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Khan Academy} & Mountain View, CA \\
\emph{Software Developer Intern} & \emph{Summer 2011}
\end{tabular*}

% Yellow Phoenix
\noindent 
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Academic Computing} & Dartmouth College, Hanover NH \\
\emph{Software Developer} & \emph{2009 to 2010}
\end{tabular*}

%% Selected Talks & Presentations
\noindent
\\
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}}
\large {\sc {Selected Talks \& Presentations}}\\
\hline
\end{tabular*}
\\

{\small
\noindent 
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{EmberConf 2014} -- \emph{Ember Data: The way forward} & Portland, OR, \emph{Mar 25, 2014} \\
\textbf{SoCoded} -- \emph{Ember.js- Building Ambitious Web Applications} & Hamburg, Germany, \emph{Sep 29, 2013} \\
\textbf{EmberFest 2013} -- \emph{Ember Data: JJ-Abrams} & Munich, Germany, \emph{Aug 29, 2013} \\
\textbf{EmberCamp 2013} -- \emph{Ember Data} & San Francisco, CA \emph{Feb 15, 2013} \\
\end{tabular*}
}

%% Education and Training
\noindent
\\
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}}
\large {\sc {Education}}\\
\hline
\end{tabular*}

%UC Berkeley
\noindent 
\\
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Dartmouth College} & \emph{September 2008 to May 2012} \\
\emph{Bachelor of Arts in Computer Science with Honors} 
\end{tabular*}

%UC Berkeley
\noindent 
\\
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Li Po Chun United World College} & \emph{September 2006 to May 2008} \\
\end{tabular*}

%% Other Activities
%% Other Activities
\noindent
\\
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}}
\large {\sc {Other Activities}}\\
\hline
\end{tabular*}

%Year One Labs
\noindent 
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{Ember Data} -- \emph{Team Member} & \emph{2013 to Present}
\end{tabular*}

%Year One Labs
\noindent 
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{MUN a smart alarm clock} --  \emph{Spring 2011}
\end{tabular*}


\end{document}
